---
title: "Habits"
author: John Doe
date: March 22, 2005
output: beamer_presentation
---

```{r echo=F}
knitr::opts_chunk$set(echo=F, warning=F, message=F)
options(xtable.comment = FALSE)
```

```{r eval=F}
rmarkdown::render('presentation.Rmd')
```

## Overview


\begin{figure}[!h]
  \centering
	
  \noindent \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{/Users/KSauby/Documents/Projects/R-Markdown-Introduction/images/overview.png}
	
\end{figure}


## Breakfast



\begin{figure}[!h]
  \centering
	
  \noindent \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{/Users/KSauby/Documents/Projects/R-Markdown-Introduction/images/workflow.png}

\end{figure}


# Citations + Google Scholar

## Set up Google Scholar, part 1

Set up Google Scholar so that it shows your BibTex formatting for each citation
This assumes that you have a Google account

## Set up Google Scholar, part 2

## Example - Addition Citations to your .bib

- Now we can look up articles on Google Scholar and *copy and paste* the BibTex citation to my "bibliography.bib" file
- Rarely do I have to write the BibTex citation from scratch

## Why Use R Markdown for your Citations/Bibliography?

- formats citations according to format of your choosing
- compiles bibliography for you
- when you re-compile your R Markdown document, the bibliography will be recreated as well
-- ensures that bibliography is up-to-date
-- no extras, no missing references

# Other Benefits of Using R Markdown

## Tables

## Tables and Figures

- R Markdown numbers the tables and figures for you so you do not have to!

## R Markdown Vs. Microsoft Word

Pros of R Markdown

- incorporate code directly into your document 
- you can hide text that you are ready to delete!

Cons of R Markdown

- track changes - not as easy to implement changes when you have to do it in R Markdown
## Bookdown Dissertation!

https://github.com/ksauby/thesisdownufl



## Resources

https://rmarkdown.rstudio.com/index.html

https://bookdown.org/yihui/rmarkdown/

## Output to Word

## Output to PDF

## Output to Multiple Formats


##


##


##


##


##



##

where to find csls
